Deep Probabilistic Models for Camera Geo-Calibration

### 2018-12-07 dissertation.tex
add bookmarks (can only view in chrome)

\usepackage[pdfauthor={Menghua Zhai},
            pdftitle={dissertation},
            bookmarks=false,
            bookmarksnumbered=true,
            bookmarksopen=true,
            breaklinks=true,
            letterpaper=true,
            linktocpage,
            pagebackref=true]{hyperref}

>>>>

\usepackage[pdfauthor={Menghua Zhai},
            pdftitle={dissertation},
            bookmarks=true,
            bookmarksnumbered=true,
            bookmarksopen=true,
            breaklinks=true,
            letterpaper=true,
            linktocpage,
            pagebackref=true]{hyperref}
